Centralized Programming for Distributed Control Planes

### 2016-01-27 paper/motivation.tex
minor to motivation

Operators today generate the BGP configuration of individual devices based on intended policy. Whether this task is done fully manually or with the aid of templates, the challenge is to decompose network-wide policies
%(e.g., prefer customer networks, or never announce a route to a certain prefix to external neighbors),
into device-level policies that collectively produce the intended behavior.
This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures. We illustrate this point using two examples based on policies that we have seen in practice.
%In the next section, we demonstrate the ease with which the
%policies can be specified using our new language \sysname.
%The next section describes how to automatically compile this specification to device-level policies.

>>>>

%Operators today generate the BGP configuration of individual devices based on intended policy. 
When generating BGP configurations, whether fully manually or aided by templates, the operators face the challenge of decomposing network-wide policies
into appropriate device-level policies.
This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures. We illustrate this point using two examples based on policies that we have seen in practice. The next section shows how \sysname allows operators to directly express these policies. 
%the ease with which the
%policies can be specified using our new language \sysname.
%The next section describes how to automatically compile this specification to device-level policies.
